### 2016-03-14 paper/icfp16-submission/semantics.tex
kill the resolve business

A \emph{normalized} value substitution is one whose co-domain is
comprised of normalized values.
%
In the sequel, we will assume and ensure that all value substitutions
are normalized.

\paragraph{Resolving Holes}
We \emph{resolve} a hole with respect to a substitution by
transitively applying the substitution as long as it contains
any holes that are defined in the substitution.
%
We write \resolve{\thole}{\tsu} to denote the the resolution
of \thole\ with respect to \tsu.
%
Note that by definition, \resolve{\thole}{\tsu} does not contain
any holes in the domain of \tsu.

>>>>

A \emph{normalized} value substitution is one whose co-domain is
comprised of normalized values.
%
In the sequel, we will assume and ensure that all value substitutions
are normalized.
%
We ensure additionally that the co-domain of a substitution does not
refer to any elements of its domain, \ie when we extend a substitution
with a new binding we apply the substitution to itself.

% \paragraph{Resolving Holes}
% We \emph{resolve} a hole with respect to a substitution by
% transitively applying the substitution as long as it contains
% any holes that are defined in the substitution.
% %
% We write \resolve{\thole}{\tsu} to denote the the resolution
% of \thole\ with respect to \tsu.
% %
% Note that by definition, \resolve{\thole}{\tsu} does not contain
% any holes in the domain of \tsu.
